### 2014-02-23 docs/seminar/evaluation.tex
adding result l2r table
random ranker

\subsection{Learning To Rank}
TODO

>>>>

\subsection{Learning To Rank}
In order to accumulate required data to achieve translators' ranking model, we conduct a survey using eight human annotators. Each question of survey represents a situation in which three translators each with four criteria are proposed. Based on \textit{total order} strategy, annotators should rate them from one to three. The accumulated data has $400$ situations consists of $1200$ annotations.

In order to apply Learning to Rank algorithms on data, we use RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib}. Each method is calculated using 10-Fold Cross-Validation by splitting the data in train, validation and test datasets. We select $5$ learning to rank methods, three pairwise and two listwise.

In order to evaluate the results, NDCG and ERR measures are selected.

In order to evaluate the results, we need to choose an evaluation measure which applies on whole the list (with $3$ items) and not a portion of that. Therefore just relevance grading evaluation measures like DCG, NDCG and ERR can be used. In current study, we use NDGC and ERR both with rank position at $3$.

TODO discussion about the results.

\begin{table}
\begin{center}
\scalebox{1.2}{
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & \textbf{0.93} & 0.832 & \textbf{0.447} & 0.373 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline
\end{tabular}
}
\caption{Results of Applying Learning to Rank Methods based on NDCG and ERR evaluation measures}
\label{table:l2rresult}
\end{center}
\end{table}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{figures/l2rdiagram.png}
\caption{Learning to Rank Results
\label{fig:l2rdiagram}}
\end{center}
\end{figure}
